---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wkpeek

<!-- badges: start -->
<!-- badges: end -->

The goal of wkpeek is to get imagery from a tile server using generic methods, with input
from a {wk} object driving the spatial query, and a background image canvas from {magick}
on which we can plot the object. 

## Installation

You can install the development version of wkpeek like so:

``` r
##remotes::install_github("mdsumner/wkpeek")
```

## Example

This is a basic example which shows you how to use a wk subset object to get a background
image as a {magick} canvas. 

```{r example}
library(wkpeek)

sql <- "SELECT geometry FROM \"ns-water_water-poly_geo\" WHERE NAME_1 = 'Mud Lake'"
url <- "/vsicurl/https://github.com/geoarrow/geoarrow-data/releases/download/v0.2.0/ns-water_water-poly_geo.parquet"
layerinfo <- vapour::vapour_layer_info(url)
geom <- wk::wkb(vapour::vapour_read_geometry(url, sql = sql), crs = layerinfo$projection$Wkt)

wk_peek(geom[32:35], border = c("hotpink", "green", "firebrick", "white"), lwd = 3)
```


Originally scoped out here as a way to toy with magick as a way to view image tiles: https://gist.github.com/mdsumner/cf11ec316f61046c363fd2a314c6ee26


## Code of Conduct
  
Please note that the wkpeek project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
